---
title: "How to use `fish_fun`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{fish_fun}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## What does the function take?

Function `fish_fun` takes a *vector* of fish names as the input variable `fish`. Users can also specify whether they want the function to return a histogram of the fish names or not. This option is achieved by calling `plot = TRUE` or `plot = FALSE`.  

## What does the function return?

In default, no histogram will be returned (`plot = FALSE`). The function will take the vector of fish names, convert it into a list, and return the most common fish, the rarest fish, and the total number of fish. If `plot = TRUE`, a histogram will be returned in addition to the above three items.

## Example

First, import the package. 
```{r}
library(mypack)
```

Second, create the vector of fish. Recall that the input of `fish_func` should be a vector of characters.
```{r}
fish = fish_data$x
```

- No histogram 

```{r}
fish_fun(fish, plot = FALSE)
```

- With histogram

```{r}
fish_fun(fish = fish, plot = TRUE)
```



